%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Reposit Power Pty Ltd} % Organisation
    {Fyshwick, Australia} % Location
    {Oct 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and maintained Python-based backend services, effectively managing system integration and data flows across complex IoT device networks, improving data accuracy and operational stability.}
        \item {Proactively identified and resolved technical issues, employing robust troubleshooting and debugging skills within Linux server environments.}
        \item {Enhanced system interdependencies management through clear documentation and proactive health checks, ensuring continuous operational performance.}
        \item {Leveraged Google Cloud Platform (GCP) for cloud computing needs, optimizing resource allocation and scaling to accommodate growing data and processing requirements.}
        \item {Collaborated closely with a cross-functional team to drive continuous learning and innovation, applying new technologies and tools to maintain a competitive edge in a rapidly evolving technological landscape.}
        \item {\textbf{Technical Skills:} Python, Linux Systems, SSH, Google Cloud Platform, Asynchronous Programming, Embedded Systems}
      \end{cvitems}
    }

  \cventry
    {Back End Developer} % Job title
    {4DATA IT} % Organisation
    {Queanbeyan, Australia} % Location
    {Jul 2023 - Oct 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborated with stakeholders to gather and clarify requirements, translating them into backend functionalities including blockchain integration and subscription-based notifications.}
        \item {Documented system architecture and performed thorough testing, ensuring seamless integration with front-end systems and meeting business expectations.}
        \item {Architected the back-end of the "ACTSmart Business Training" platform using Node.js, Express.js, and MongoDB, implementing features such as a login system, administrative privileges, a quiz system, and a feedback system to enhance user engagement and experience.}
        \item {Leveraged Docker and Docker Compose for efficient deployment and scaling of web applications, fostering agile development processes and facilitating continuous integration/continuous deployment (CI/CD).}
        \item {\textbf{Technical Skills:} Node.js, Express.js, MongoDB, Blockchain Integration, Web Push API, Docker, Docker Compose}
      \end{cvitems}
    }

    
  \cventry
    {Research Assistant} % Job title
    {QuantEcon} % Organisation
    {Canberra, Australia} % Location
    {Apr 2023 - Aug 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted research and compiled data for multiple projects under John Stachurski's supervision, ensuring accuracy and integrity using Python.}
        \item {Maintained and updated department databases, evaluating and investigating economic, financial, and statistical relationships to contribute to research initiatives and analyze economic time series data.}
        \item {Collaborated with the research team to summarize findings, present information, and advance project goals.}
        \item {\textbf{Technical Skills:} Python, Linux, Jax.}
      \end{cvitems}
    }
  
  \cventry
    {Full Stack Developer \& Scrum Master} % Job title
    {Jemma} % Organisation
    {Canberra, Australia} % Location
    {Jul 2022 - May 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Effectively communicated, both orally and in writing, with peers, supervisors, and commercial clients/stakeholders.}
        \item {Planned and documented the project throughout its development.}
        \item {Served as Scrum Master, facilitating effective communication among developers, stakeholders, and clients, clearly articulating business needs into IT requirements.}
        \item {Managed agile processes using Jira, ensuring timely project delivery and continuous alignment with client expectations.}
        \item {\textbf{Technical Skills:} Flutter, Firebase, Python, Dart, SQL.}
        \item {\textbf{Soft Skills:} Teamwork, Time Management, Communication, Presentation Skills.}
      \end{cvitems}
    }

  \cventry
    {Product manager - Commercial products} % Job title
    {ByteDance} % Organisation
    {Beijing} % Location
    {Oct 2021 - Jan 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Enhanced CRM system functionality, streamlining data access and visualization to significantly improve operational efficiency and user experience.}
        \item {Engaged directly with international stakeholders to capture business requirements clearly and accurately, converting these into well-documented technical specifications and prototypes.}
        \item {Grant Cost Field Addition: Streamlined the CRM system by enabling direct grant cost queries in the performance page, previously retrieved only from the TikTok ads platform. This update reduced manual data retrieval efforts by 20\% and improved overall productivity.}
      \end{cvitems}
    }

  % \cventry
  %   {Global Product Operations - Commercial Products} % Job title
  %   {ByteDance} % Organisation
  %   {Beijing} % Location
  %   {Jul 2021 - Oct 2021} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Managed online Q\&A for customers and established FAQ systems for both the performance and CRM sectors, streamlining user support and identifying recurring issues for product team feedback.}
  %       \item {Conducted user acceptance tests and monitored data quality, providing notifications when SLA compliance failed to maintain service standards.}
  %       \item {Authored and published in-depth micro-blogs to educate users on the 3M system and led the creation of mini-courses and biweekly training sessions to familiarize users with system features and functionalities.}
  %     \end{cvitems}
  %   }

  \cventry
    {Operation and Maintenance Engineer} % Job title
    {TitanOS} % Organisation
    {WuHan} % Location
    {Nov 2019 - Jan 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Deployed, configured, and maintained Docker-based container platforms, ensuring smooth operations and up-to-date systems.}
        \item {Gained hands-on experience in operating and maintaining Kubernetes container management framework, enhancing overall container orchestration capabilities.}
        \item {\textbf{Technical Skills:} Docker, Kubernetes, Linux}
      \end{cvitems}
    }

\end{cventries}
